---
title: "Alcohol vs Seat choice"
author: "Diego Martinez"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

## Introduction: 
Our goal is to answer the following questions. Examining if the row of seats
you sit in, determines the amount of alcohol you consume. 

## Is there a difference between the alcohol consumed between the row  you choose to sit in?

$H_0$: There is no difference between which row you sit in and the amount of alcohol consumed. There is no relationship between the two.   
$H_A$ There is a difference between which row you sit in and the amount of 
alcohol is consumed based off of the cultivation method (data table)  


## Methods 

We are examining the amount of alcohol consumed (numerical) by examining the
3 different types of seats: front, middle, and back(categorical). We'll be using
a T-test to compare alcohol consumption in 3 groups. 


## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

The amount of alcohol drank per row (according to the box plot) is significantly 
different. As we can see, the median for the back row is higher than the total
amount of alcohol drank in the front row and middle row. There was few alcohol 
drank in the front and middle row. Although, the middle row did drink more. The 
middle row had the most outliers but it's still no where compared to the back 
row. The back row has 2 outliers that drank significantly anove the median. 

### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The results from the fancy box plot and the regular box plot are fairly similar. 
The back row still drinks the most by far. The amount of outliers, median range, and mean all stayed the same.

## Numerical Descriptive Results

```{r}
favstats(alcohol~Seat,data=davisdata)
```
The back seat has a median of 4: much greater than the other 2. The maximum for the back is 55. That's 35 more than the front and 20 more than the back. The overall average for the back is 9.6. Much higher than the other two seats. From this data, the back seat significantly drinks the most alcohol out of all 3 seats. Since the median, max, and mean are all greater than the other 2 seats. 

## Inferential Results

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
We can infer that the P-value is .000116. From the AOV, we can reject the 
null hypothesis due to how small the p-value is. If the p-value is not.05 or higher, we can reject it due to how small the chances are. In every problem, we
know we're accurate when we can reject the null hypothesis. In this case, we did. 
There is a difference between how much alcohol is consumed in every seat. 

```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 15, 2, 2))
plot(TukeyHSD(model1),las=2)
```

There is clearly a difference. The familiies confidence level doesn't even reach 0 for (Front-Back) and (Middle-Back). The clear winner for the tukey HSD test is the (Middle-Front). Since its range goes from -2.5 to over 5. In second place, is 
the (Middle-Back). Its range is he second closest to reaching 0. 

## Conclusion 

The seat category and amount of alcohol consumed is different. The back seat median, max, and mean are all greater than the other 2 seats. The median is different by at least 3. The mean is different by at least 6.4. The max is different by at least 35. We rejected the null hypothesis after seeing the results of the AOV. There is clearly a difference. People in the back seat drink the most, people in the middle seat drink the 2nd most, and people in the front seat drink the least.

