---
title: "Alcohol vs Seat choice"
author: "Diego Martinez"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

## Introduction: 
Our goal is to answer the following questions. Examining if the row of seats
you sit in, determines the amount of alcohol you consume. 

## Is there a difference between the alcohol consumed between the row  you choose to sit in?

$H_0$: There is no difference between which row you sit in and the amount of alcohol consumed. There is no relationship between the two.   
$H_A$ There is a difference between which row you sit in and the amount of 
alcohol is consumed based off of the cultivation method (data table)  


## Methods 

We are examining the amount of alcohol consumed (numerical) by examining the
3 different types of seats: front, middle, and back(categorical). We'll be using
a T-test to compare alcohol consumption in 3 groups. 


## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```



### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```



## Numerical Summarys 

## Inferential Tests

## Conclusion 



